---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r ,warning=FALSE,message=FALSE}
library(readxl)
library(dplyr)
collegehookup <- read_excel("collegehookup.xlsx")
poisson.model <- glm(hookup_sum ~Gender+Age+Hisp+Black+Asian+BMI+
                       BMI2+college_dad + college_mom + hookup_highschool+
                       Siblings + ParentsDivorce,
                     collegehookup, family = poisson(link = "log"))
summary(poisson.model) 
```
I think some of the coefficients can be explained as following:\
1. The positive hookup_highschool coefficient is because if there is hookup in\
high school, students would be far more familiar with the process of hookup,\
making hookup much easier.\
2. The negative college_mom coefficient is because if mother has a college degree,\
the control of parents toward the youngling would be stronger,\
which makes it harder for hookup.\
3. The positive Siblings coefficient is because having more sibling can improve\ social ability, which makes it easier for hookup.\
4. The positive ParentsDivorce coefficient is because the control of parent toward children\
would be alleviated if there is divorce.\
The following is going to create the variable "peer_effect".
```{r ,warning=FALSE,message=FALSE}
library(dplyr)
df <- data.frame(collegehookup)
df["peer_effect"] <- -1
df <- df[order(df$greek_group),]
this_row = 1
for( i in c(1:26)){
  temp_df <- filter(df, greek_group == i)
  if((!is.null(temp_df))){
    club_total_times = sum(temp_df$hookup_sum)
    club_menber_num = nrow(temp_df)
    if(club_menber_num>1){
      for( j in c(1:nrow(temp_df))){
        df[this_row,]["peer_effect"] <-
          (club_total_times-df[this_row,]["hookup_sum"])/(club_menber_num-1)
        this_row <- this_row+1
      }
    }
    else{
      this_row <- this_row+ club_menber_num
    }
  } 
}
df<-df[!(df$peer_effect==-1 ),]
poisson.model2 <- glm(hookup_sum ~ peer_effect+Gender+Age+Hisp+Black+
                        Asian+BMI+BMI2+college_dad + college_mom +
                        hookup_highschool+Siblings + ParentsDivorce,
                     df, family = poisson(link = "log"))
summary(poisson.model2)
```
When there is only one student in a club, there is no way to define peer_effect.\
We remove the data from the dataset.\
The p-value of peer_effect 0.507813.\
As a result, we conclude that there is no peer effect.\
```{r ,warning=FALSE,message=FALSE}
summary(df$peer_effect)
```
